\documentclass[a4paper,12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{parskip}
\usepackage{graphicx}
\usepackage{hyperref}
\geometry{margin=1in}

\begin{document}

\title{CSUN Comp584 HW3 Accessibility Findings}
\date{October 2025}
\maketitle

\section{Button Approach}
I explored two approaches for buttons: single button vs. multiple buttons.
\begin{itemize}
    \item \textbf{Single Button Pros}: Simpler design, less clutter, clear call-to-action. \textbf{Cons}: Limits user options, may reduce engagement.
    \item \textbf{Multiple Buttons Pros}: Offers more actions (e.g., "Learn More" and "Join Now"), increases engagement. \textbf{Cons}: Can overwhelm in small email space.
\end{itemize}
I chose two buttons, centered with extra padding and margin (15px padding, 10px margin) for clickability, balancing engagement and simplicity.

\section{Accessibility Testing}
I tested my email page and frequented sites (csun.edu, google.com) using:
\begin{itemize}
    \item \textbf{WAVE}: Flagged no missing alt text on my email (all images have alt attributes). On csun.edu, found low contrast on some links.
    \item \textbf{Lighthouse}: Scored my email 85/100 for accessibility due to table-based layout; suggested adding ARIA roles. Google.com scored 95/100.
    \item \textbf{Screen Reader (VoiceOver)}: My email's headings and links were navigable; image alt text was read correctly. On csun.edu, some images lacked alt text.
\end{itemize}
\textbf{Pros}: Tools are easy to use, identify clear issues. \textbf{Cons}: Screen readers require setup; WAVE may miss nuanced issues.

\section{Screenshots}
% Placeholder for screenshots; replace with actual images if possible
\textbf{My Email Page}: [Describe screenshot of email page showing buttons and layout.] \\
\textbf{CSUN.edu WAVE Report}: [Describe screenshot of WAVE results on csun.edu.]

\section{Conclusion}
The table-based layout ensures email compatibility, and buttons are accessible with proper spacing. Accessibility tools helped improve my design and revealed issues on other sites.

\end{document}